\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-11-16 eg6-letters/NIM/review-1/review-1.tex
update the response to questions 18 and 21

\item Please detail a little bit more the procedure to remove the oscillatory 
   noise. It says "event by event and channel by channel": if the ADC threshold 
   is passed then a noise level is subtracted? If so, how is it calculated?\\
\textcolor{red}{Nathan, Can you work on it. }

@@

\item < dE/dx > is computed here as corrected Etot divided total track length. 
   Usually the mean dE/dx is computed with the truncated mean of the specific 
   energy losses of each hit. Isn't it possible to compute it like this here? 
   dx for each hit can be (maybe) computed from the difference in the hit 
   times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
\textcolor{blue}{Maybe this would improve our calculations for dEdx by few 
percent, but a precise hits ordering is needed to compute dEdx as you suggest, 
which is not available in our setting.}

>>>>

\item Please detail a little bit more the procedure to remove the oscillatory 
   noise. It says "event by event and channel by channel": if the ADC threshold 
   is passed then a noise level is subtracted? If so, how is it calculated?\\
\textcolor{blue}{The oscillatory noise was removed just by rejecting all hits 
from a channel if too many of its hits fall on the noise curve in a given 
event. No threshold/pedestal concept, just hit rejection if it looks like 
noise. }

@@

\item < dE/dx > is computed here as corrected Etot divided total track length. 
   Usually the mean dE/dx is computed with the truncated mean of the specific 
   energy losses of each hit. Isn't it possible to compute it like this here? 
   dx for each hit can be (maybe) computed from the difference in the hit 
   times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
\textcolor{blue}{We actually did compute dEdx with  path-length and ADC- 
truncations, and a linear fit to ADC vs path-length to get slope and fit 
quality and dedx from fit. Unfortunately, it never seemed to give us much 
improvement compared to Sum $dE_{i}$/Sum $dx_{i}$. }
